The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-09 paper.tex
update

  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0--1.2$ Myr,\
  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
  $8\times10^{55}$ erg and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

@@

  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
  cut at various galactic latitudes (as labelled), compared with the observation (black).\

  \Cref{fig_xray-map} is quite revealing in several ways.\

>>>>

  The bipolar jets are constantly ejected from a cylindrical source within a jet duration time $t=0$ -- $1.2$ Myr,\
  allowing the total ejected energy $1.2\times10^{56}$ erg is between\
  $8\times10^{55}$ -- $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

@@

  \Cref{fig__x-ray-profile-0.8keV-000} displays the simulated count rate profiles (red)\
  in the same energy band as \Cref{fig__xray_0.8keV_angle_000}\
  cut at various galactic latitudes (as labelled), compared with the observation (black).\
  \Cref{fig_xray-map} is quite revealing in several ways.\
